DOpElib:\\ Differential Equations and Optimization Environment

### 2016-04-01 Examples/Documentation/introduction.tex
Removed warnings when compiling with deal 8.4.0

When installing \texttt{deal.II} you should take care to configure 
it to use UMFPACK, i.e.,\\
\texttt{./configure --with-umfpack}
in version up to 7.3.0. From 8.0.0 on, deal.II is compiled with 
cmake, which makes the inclusion of external packages easier.
Detailed installing instructions for deal.II (here the last version
8.1.0) can be found on\\ 
\texttt{http://www.dealii.org/8.1.0/readme.html}.

>>>>

When installing \texttt{deal.II} you should take care to configure 
it to use UMFPACK, i.e.,\\
\texttt{./configure --with-umfpack}
in version up to 7.3.0. From 8.0.0 on, deal.II is compiled with 
cmake, which makes the inclusion of external packages easier.
Detailed installing instructions for deal.II can be found on\\ 
\texttt{http://www.dealii.org/}.

In deal.II 8 and newer a configuration of deal.II working with \texttt{DOpElib} can be done with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install -DDEAL_II_WITH_UMFPACK=true -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags

\begin{lstlisting}
-DDEAL_II_WITH_TRILINOS=true -DTRILINOS_DIR=[path to trilinos]
\end{lstlisting}
